---
title: "stockX_analysis_Nike"
author: "Anson"
date: "2023-06-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Import Libraries
library(tidyverse)
library(dplyr)
library(ggplot2)
library(here)
library(plotly)

```

#Load in Data Frame, using read.csv(), and here() fucntion
```{r}
stockX_data <- read.csv(here("StockX-Data-Contest-2019-3.csv"))

```

#Filter() by Brand to select Nike. Select() to choose Sneaker.Name, Order.Date, Sale.Price
```{r}
stockX_data_nike <- stockX_data %>%
  filter(Brand == "Off-White") %>%
  select(Sneaker.Name, Order.Date, Sale.Price,)
```

#Use gsub() function to remove Nike and Off-White from names, and charachters preventing it from being a numeric. Use as.numeric() to convert the Sale.Price column to numeric. Use mdy() function to convert the Order.Date column to a date
```{r}
stockX_data_nike$Sneaker.Name <- gsub("^Nike-|-Off-White", "", stockX_data_nike$Sneaker.Name)

stockX_data_nike$Sale.Price <- gsub("\\$|\\,", "", stockX_data_nike$Sale.Price)

stockX_data_nike$Sale.Price <- as.numeric(stockX_data_nike$Sale.Price)

stockX_data_nike$Order.Date <- mdy(stockX_data_nike$Order.Date)
```

#Use ggplot() to visualize Nike sales date for the year. Using geom_point() as the main graph. Use ggplotly() from plotly package to make the graph interactive, in order to view specific sale date and price. 
```{r}
nike_graph <- stockX_data_nike %>%
  arrange(desc(Sneaker.Name))
  
nike_graph <- ggplot(stockX_data_nike, aes(x = Order.Date, y = Sale.Price, color = Sneaker.Name)) +
  geom_point()+
  facet_wrap(~stockX_data_nike$Sneaker.Name) +
  labs(x = "Order Date", y = "Sale Price", title = "Nike Off-White StockX Sales")

interactive_nike_graph <- ggplotly(nike_graph)
interactive_nike_graph
```







#Filter() for Jordan 1 Uni Blue, select() relevant columns
```{r}
stockX_data_nike2 <- stockX_data %>%
  filter(Sneaker.Name == "Air-Jordan-1-Retro-High-Off-White-University-Blue") %>% 
  select(Sneaker.Name, Order.Date, Release.Date, Sale.Price)

```

#remove charachters using gsub(), convert class using as.numeric() and mdy() for date columns
```{r}
stockX_data_nike2$Sale.Price <- gsub("\\$|\\,", "", stockX_data_nike2$Sale.Price)

stockX_data_nike2$Sale.Price <- as.numeric(stockX_data_nike2$Sale.Price)

stockX_data_nike2$Release.Date <- mdy(stockX_data_nike2$Release.Date)
stockX_data_nike2$Order.Date <- mdy(stockX_data_nike2$Order.Date)
```

#filter() for 3 month range
```{r}
stockX_data_nike2 <- stockX_data_nike2 %>%
  filter(Order.Date >= "2018-06-23" & Order.Date <= "2018-09-23") %>%
  select(Sneaker.Name, Order.Date, Sale.Price)
```

#visualize the graph using scatterplot geom_point
```{r}
nike_j1unc_graph <- ggplot(stockX_data_nike2, aes(Order.Date, Sale.Price)) +
  geom_point(color = "lightblue") +
  geom_smooth()+
  labs(x = "Order Date", y = "Resell Price", title = "Air Jordan 1 Off-White Univeristy Blues Sales", subtitle = "3 Month Range")+
 theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))
nike_j1unc_graph
```


