---
title: "stockX_analysis_1"
author: "Anson"
date: "2023-06-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Import Libraries
library(tidyverse)
library(dplyr)
library(ggplot2)
library(here)
library(gridExtra)

```

#Load in Data Frame, using read.csv(), and here() fucntion
```{r}
stockX_data <- read.csv(here("StockX-Data-Contest-2019-3.csv"))

```

#Find unique values of Brand column in df, using unique() function
```{r}
unique(stockX_data$Brand)

```

#Find number of unique values in brand column, using table() function
```{r}
table(stockX_data$Brand)

```

#Select Yeezy 350 models by index using the grep() function, grep returns the index. Select 350 by using splice() fucntion with the saved index Yeezy_350
```{r}
Yeezy_350 <- grep("350", stockX_data$Sneaker.Name)

stockX_data <- stockX_data %>%
  slice(Yeezy_350)

tail(stockX_data) #checks to see if last obsv contain 350

```

#Use unique() fucntion and table() fucntion to check which 350 models are in the df
```{r}
unique(stockX_data$Sneaker.Name)
table(stockX_data$Sneaker.Name)
```

#Select relevant columns:[3]Sneaker.Name, [4]Sale.Price, [5]Retail.Price using select() function. Arrnage using arrange() function
```{r}
stockX_data <- stockX_data %>%
  select(Sneaker.Name, Sale.Price, Retail.Price) %>%
  arrange(Sneaker.Name)

```

#Remove" $ "and" , " from the sales price and retail price column using gsub() funtion. Convert class of Sales.Price and Retail.Price column. "charachter" to "numeric".using as.numeric() function
```{r}

stockX_data$Sale.Price <- gsub("\\$", "", stockX_data$Sale.Price)
stockX_data$Sale.Price <- gsub("\\,", "", stockX_data$Sale.Price)
stockX_data$Retail.Price <- gsub("\\$", "", stockX_data$Retail.Price)

stockX_data$Sale.Price <- as.numeric(stockX_data$Sale.Price)
stockX_data$Retail.Price <- as.numeric(stockX_data$Retail.Price)

```

#Use group_by() function and gorup by Sneaker.Name to refine obersavtions and use summarize() function and sum() function to caluclate total resell price and total retail price
```{r}
stockX_data <- stockX_data %>%
  group_by(Sneaker.Name) %>%
  summarize(Total.Resell.Price = sum(Sale.Price), Total.Retail.Price = sum(Retail.Price))

```

#Graph of Total Resell Price using geom_col()
```{r}
stockX_resell_graph_350 <- ggplot(data = stockX_data, aes(Sneaker.Name, Total.Resell.Price))+
  geom_col() +
  theme_classic()+
  coord_flip() +
  scale_y_continuous(labels = scales::comma_format()) +
  geom_text(aes(label = Total.Resell.Price), hjust = -0.05, size = 3)+
  labs(y = "Total Resell Price", x = "Colorway", title = "StockX Sales 2019", subtitle = "Adidas Yeezy Boost 350") 

stockX_resell_graph_350
```
#Graph of Total Retail Price using geom_col()
```{r}
stockX_retail_graph_350 <- ggplot(data = stockX_data, aes(Sneaker.Name, Total.Retail.Price))+
  geom_col() +
  theme_classic()+
  coord_flip() +
  scale_y_continuous(labels = scales::comma_format()) +
  geom_text(aes(label = Total.Retail.Price), hjust = -0.05, size = 3)+
  labs(y = "Total Retail Price", x = "Colorway", title = "StockX Sales 2019", subtitle = "Adidas Yeezy Boost 350") 

stockX_retail_graph_350
```

#
```{r}
grid.arrange(stockX_resell_graph_350, stockX_retail_graph_350, ncol = 1)

```

