---
title: "stockX_analysis_1"
author: "Anson"
date: "2023-06-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Import Libraries
library(tidyverse)
library(dplyr)
library(ggplot2)
library(here)
library(gridExtra)
library(plotly)

```

#Load in Data Frame, using read.csv(), and here() fucntion
```{r}
stockX_data <- read.csv(here("StockX-Data-Contest-2019-3.csv"))

```

#Find unique values of Brand column in df, using unique() function
```{r}
#unique(stockX_data$Brand)

```

#Find number of unique values in brand column, using table() function
```{r}
#table(stockX_data$Brand)

```

#Select Yeezy 350 models by index using the grep() function, grep returns the index. Select 350 by using splice() fucntion with the saved index Yeezy_350
```{r}
Yeezy_350 <- grep("350", stockX_data$Sneaker.Name)

stockX_data <- stockX_data %>%
  slice(Yeezy_350)

#tail(stockX_data) #checks to see if last obsv contain 350

```

#Use unique() fucntion and table() fucntion to check which 350 models are in the df
```{r}
#unique(stockX_data$Sneaker.Name)
#table(stockX_data$Sneaker.Name)
```

#Select relevant columns:[3]Sneaker.Name, [4]Sale.Price, [5]Retail.Price using select() function. Arrnage using arrange() function
```{r}
stockX_data <- stockX_data %>%
  select(Sneaker.Name, Sale.Price, Retail.Price) %>%
  arrange(Sneaker.Name)

```

#Remove" $ "and" , " from the sales price and retail price column using gsub() funtion. Convert class of Sales.Price and Retail.Price column. "charachter" to "numeric".using as.numeric() function
```{r}

stockX_data$Sale.Price <- gsub("\\$", "", stockX_data$Sale.Price)
stockX_data$Sale.Price <- gsub("\\,", "", stockX_data$Sale.Price)
stockX_data$Retail.Price <- gsub("\\$", "", stockX_data$Retail.Price)

stockX_data$Sale.Price <- as.numeric(stockX_data$Sale.Price)
stockX_data$Retail.Price <- as.numeric(stockX_data$Retail.Price)

```

#Use group_by() function and gorup by Sneaker.Name to refine obersavtions and use summarize() function and sum() function to caluclate total resell price and total retail price
```{r}
stockX_data <- stockX_data %>%
  group_by(Sneaker.Name) %>%
  summarize(Total.Resell.Price = sum(Sale.Price), Total.Retail.Price = sum(Retail.Price))

```


#Graph of Total Resell Price using geom_col()

#Updated graph, added geom_col(aes for Total.Retail.Price and Total.Resell.Price) This allows for a stacked graph rather than the grid.arrange() scale_fill_manual() sets color
```{r}
stockX_resell_graph_350 <- ggplot(data = stockX_data, aes(Sneaker.Name))+
  geom_col(aes(y = Total.Resell.Price, fill = "Total.Resell.Price"), position = "stack") +
  geom_col(aes(y = Total.Retail.Price, fill = "Total.Retail.Price"), position = "stack") +
  scale_fill_manual(values = c("Total.Retail.Price" = "blue", "Total.Resell.Price" = "forestgreen")) +
  coord_flip() +
  scale_y_continuous(labels = scales::comma_format()) +
  #geom_text(aes(label = Total.Resell.Price), hjust = -0.05, size = 3)+
  labs(y = "Price", x = "Colorway", title = "StockX Sales 2019", subtitle = "Adidas Yeezy Boost 350") 

interactive_350_graph <- ggplotly(stockX_resell_graph_350)
interactive_350_graph

```
#Graph of Total Retail Price using geom_col()
```{r}
#stockX_retail_graph_350 <- ggplot(data = stockX_data, aes(Sneaker.Name, Total.Retail.Price))+
 # geom_col() +
#  theme_classic()+
#  coord_flip() +
#  scale_y_continuous(labels = scales::comma_format()) +
#  geom_text(aes(label = Total.Retail.Price), hjust = -0.05, size = 3)+
#  labs(y = "Total Retail Price", x = "Colorway", title = "StockX Sales 2019", subtitle = "Adidas Yeezy Boost 350") 

#stockX_retail_graph_350
```

#
```{r}
#grid.arrange(stockX_resell_graph_350, stockX_retail_graph_350, ncol = 1)

```







#Line graph price/date

```{r}
stockX_data <- read.csv(here("StockX-Data-Contest-2019-3.csv"))

```

#rename, filter() by Brand to select Yeezy, select() relevant columns, Order.Date, Sneaker.Name, Sale.Price
```{r}
stockX_yeezy_pd <- stockX_data %>%
  filter(Brand == " Yeezy") %>%
  select(Order.Date, Sneaker.Name, Sale.Price)

```

#Use gsub() to remove $ and ,. Then use as.numeric() to convert the Sale.Price category to numeric. 
```{r}
stockX_yeezy_pd$Sale.Price <- gsub("\\$|\\,", "", stockX_yeezy_pd$Sale.Price)
stockX_yeezy_pd$Sale.Price <- as.numeric(stockX_yeezy_pd$Sale.Price)
stockX_yeezy_pd$Order.Date <- mdy(stockX_yeezy_pd$Order.Date)
#stockX_yeezy_pd$Sneaker.Name <- gsub("\\$|\\,", "", stockX_yeezy_pd$Sale.Price)
```

#Filter() Order.Date for time period of two weeks before Christmas using operators <=, >=, &
```{r}
stockX_yeezy_pd <- stockX_yeezy_pd %>%
  filter(Order.Date >= "2018-12-13" & Order.Date <= "2018-12-24" )
  
```

#Use ggplot() to create a line graph, geom_line(). Similiar to Nike graph usuing facet_wrap() and ggplotly()
```{r}
yeezy_graph <- ggplot(stockX_yeezy_pd, aes(x = Order.Date, y = Sale.Price, color = Sneaker.Name)) +
  geom_line() +
  labs(x = "Order Date", y = "Sale Price", title = "Yeezy Sales 2 Weeks before Christmas") +
  facet_wrap(~Sneaker.Name)

interactive_yeezy_graph <- ggplotly(yeezy_graph)
interactive_yeezy_graph
```







#OG: Visual of only the V1 350
```{r}
stockX_data <- read.csv(here("StockX-Data-Contest-2019-3.csv"))

```

#Filter() Brand, and use &, use !grepl() to select everything but V2 and select() the relevant columns
```{r}
#stockX_V2_el <- grep("V2", stockX_data$Sneaker.Name)

#stockX_V2 <- stockX_data %>%
#  slice(stockX_V2_el) 
#stockX_V2

stockX_V1 <- stockX_data %>%
  filter(Brand == " Yeezy" & !grepl("V2", stockX_data$Sneaker.Name)) %>%
  select(Sneaker.Name, Sale.Price, Buyer.Region)

stockX_V1$Sale.Price <- gsub("\\$|\\,", "", stockX_V1$Sale.Price)
stockX_V1$Sale.Price <- as.numeric(stockX_V1$Sale.Price)

```

#scatter plot visual displaying the resell price, of V1 models per State
```{r}
V1_graph <- ggplot(stockX_V1, aes(x = Buyer.Region, y = Sale.Price, color = Sneaker.Name, size = Sale.Price)) +
  geom_point()+
  theme(axis.text.x = element_text(angle = 90, hjust =1))+
  labs(x = "State", y = "Resell Price", title = "V1 Sales per State", color = "Colorway Name", size = "")

interactive_V1 <- ggplotly(V1_graph)
interactive_V1
```
